Microxanox: an R package for simulating an aquatic \(MICR\)obial ecosystem that can occupy \(OX\)ic or \(ANOX\)ic states.

### 2022-06-07 inst/manuscript/manuscript_microxanox.tex
Ready for final read-through

  \begin{abstract}
  Ca. 100 words.
  \end{abstract}
    \begin{keyword}
    reproducibility; regime shift; \sep 
    reproducibility; regime shift;
  \end{keyword}

@@

\begin{itemize}
\tightlist
\item
  \textbf{\textcolor{red}{update links}}
\item[$\boxtimes$]
  \sout{\textbf{\textcolor{red}{update cross references}}}
\item
  \textbf{\textcolor{red}{check keywords}}
\item[$\boxtimes$]
  \sout{\textbf{\textcolor{red}{add more references}}}
\item
  \textbf{\textcolor{red}{expand on Impact and Conclusion section}}
  \pagebreak
\end{itemize}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0483}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4138}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.5379}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\centering
\textbf{Nr.}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Code metadata description}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Please fill in this column}
\end{minipage} \\
\midrule()
\endhead
C1 & Current code version & v0.9.0 \\
C2 & Permanent link to code/repository used for this code version &
\url{https://github.com/UZH-PEG/microxanox} \\
C3 & Code Ocean compute capsule & \\
C4 & Legal Code License & CC BY 4.0 \\
C5 & Code versioning system used & git \\
C6 & Software code languages, tools, and services used &
\href{https://cran.r-project.org/index.html}{R} \\
C7 & Compilation requirements, operating environments &
\href{https://cran.r-project.org/index.html}{R (\textgreater= 4.1.0)} \\
& & magrittr \\
& & tibble \\
& & ggplot2 \\
& & patchwork \\
& & grDevices \\
& & stats \\
& & mgcv \\
& & deSolve \\
& & dplyr \\
& & tidyr \\
& & stringr \\
& & multidplyr \\
& & \\
& & \\
& & \\
& & \\
& & \\
C8 & If available Link to developer documentation/manual &
\textcolor{red}{TO BE ADDED} \\
C9 & Support email for questions & Rainer.Krug@uzh.ch;
Rainer@krugs.de \\
\bottomrule()
\end{longtable}

>>>>

  \begin{abstract}
  \(Microxanox\) is an R package to simulate a three functional group
  system (cyanobacteria, phototrophic sulfur bacteria, and
  sulfate-reducing bacteria) with four chemical substrates (phosphorus,
  oxygen, reduced sulfur, and oxidized sulfur) osing a set of ordinary
  differential equations. Simulations can be run individually or over a
  parameter range, to find stable states. The model features multiple
  species per functional group, where the number is only limited by
  computational constraints. The R package is constructed in such a way,
  that the results contain the input parameter used, so that a saved
  results can be loaded again and the simulation be repeated.
  \end{abstract}
    \begin{keyword}
    reproducibility \sep regime shift \sep stable state \sep 
    ordinary differential equations
  \end{keyword}

@@

\begin{itemize}
\tightlist
\item
  \textbf{\textcolor{red}{update links}}
\item[$\boxtimes$]
  \sout{\textbf{\textcolor{green}{update cross references}}}
\item[$\boxtimes$]
  \sout{\textbf{\textcolor{green}{add abstract}}}
\item[$\boxtimes$]
  \sout{\textbf{\textcolor{green}{check keywords}}}
\item[$\boxtimes$]
  \sout{\textbf{\textcolor{green}{add more references}}}
\item[$\boxtimes$]
  \sout{\textbf{\textcolor{green}{expand on Impact section}}}
\item[$\boxtimes$]
  \sout{\textbf{\textcolor{green}{expand on Conclusion section}}}
  \pagebreak
\end{itemize}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0483}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4138}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.5379}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\centering
\textbf{Nr.}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Code metadata description}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Please fill in this column}
\end{minipage} \\
\midrule()
\endhead
C1 & Current code version & v0.9.0 \\
C2 & Permanent link to code/repository used for this code version &
\url{https://github.com/UZH-PEG/microxanox} \\
C3 & Code Ocean compute capsule & \\
C4 & Legal Code License & CC BY 4.0 \\
C5 & Code versioning system used & git \\
C6 & Software code languages, tools, and services used &
\href{https://cran.r-project.org/index.html}{R} \\
C7 & Compilation requirements, operating environments &
\href{https://cran.r-project.org/index.html}{R (\textgreater= 4.1.0)} \\
& & magrittr \\
& & tibble \\
& & ggplot2 \\
& & patchwork \\
& & grDevices \\
& & stats \\
& & mgcv \\
& & deSolve \\
& & dplyr \\
& & tidyr \\
& & stringr \\
& & multidplyr \\
C8 & If available Link to developer documentation/manual &
\textcolor{red}{TO BE ADDED} \\
C9 & Support email for questions & Rainer.Krug@uzh.ch;
Rainer@krugs.de \\
\bottomrule()
\end{longtable}
